Commutative Character Sheaves, with an application to generic types for supercuspidal representations

### 2015-08-26 followup.tex
Added an alternate characterization of commutative character sheaves.
Still working on descent and invariance.

Recall \cite{cunningham-roe:13a}*{Def. 1.1} that a character sheaf on $G$ is a triple $\cs{L} \ceq (\gcs{L}, \mu, \phi)$,
where $\gcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, $\mu : \bm^* \gcs{L} \to \LxL$ is an isomorphism
of sheaves on $\bG \times \bG$, and $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an isomorphism of sheaves on $\bG$.
In \emph{loc. cit.}, $G$ was assumed to be commutative, but the same definition makes sense for non-commutative $G$.
We will denote the category of character sheaves on $G$ by $\CS(G)$.
\todo{I think we should hold the term `character sheaves for G', when $G$ is not commutative, in reserve, and not use it here for non-commutative $G$. So I might advocate going back to the full definition here.\\ -CC}

@@

@@

Let $G$ be a smooth group scheme.
Let $G\der \hookrightarrow G$ denote the smooth, closed subgroup generated by the commutator morphism $c: G\times G \to G$ given by $c(x,y) = xyx^{-1}y^{-1}$; see \cite{SGA3}*{{VI}$_B$, 7.2}.

 \begin{theorem}\label{thm:descent}
 Let $G$ be a smooth group scheme over $\Fq$ 
 and let $q : G \to G\ab$ be its abelianization. 
 Suppose $G\der$ is geometrically connected 
 and that $q: G \to G\ab$ is a smooth $G\der$ bundle.
Then
\[
q^*:  \CCS(G\ab) \longrightarrow \CCS(G)
\]
is an equivalence of rigid monoidal categories.
  \end{theorem}

\begin{proof}
The quotient $q : G \to G\ab$ is the coequalizer of left $G\der$-multiplication $n : G\der\times G \to G$ and projection $p : G\der\times G \to G$, in the category of smooth group schemes.
\[
\begin{tikzcd}
G\der\times G
 \arrow{r}[shift left]{m}
  \arrow{r}[shift right,swap]{p}
&
G 
\arrow{r}{q}
& 
G\ab
\end{tikzcd}
\]
In particular, $n$, $p$ and $q$ are all smooth morphisms of relative dimension $\dim G\der$.

Let $\CCS_{G\der}(G)$ be the category of commutative character sheaves $\cs{L}$ on $G$ equipped with an isomorphism $n^*\cs{L} \to p^*\cs{L}$ satisfying canonical coherence conditions.
Then $q^* : \CCS(G\ab) \to \CCS(G)$ factors through $\CCS_{G\der}(G)$. 
\[
\begin{tikzcd}
\CCS(G\der \times G)
& \arrow{l}[shift left,swap]{n^*}
  \arrow{l}[shift right]{p^*}
\CCS(G) 
&&\arrow{ll}[swap]{q^*} 
\CCS(G\ab) \arrow{dl}{\text{comparison}}\\
&& \arrow{ul}{\text{forget}} \CCS_{G\der}(G) & 
\end{tikzcd}
\]
To see this, let $\cs{E}$ be a commutative character sheaf on $G\ab$ and observe that $q^* \cs{E}$ is equipped with a canonical isomorphism $n^*(q^* \cs{E}) \to p^*(q^* \cs{E})$ given by
\[
n^* (q^*\cs{E}) \iso (q\circ n)^* \cs{E} = (q\circ p)^* \cs{E} \iso p^* (q^*\cs{E}).
\]
Moreover, since $q : G \to G\ab$ is a smooth principal $G\der$-bundle and $G\der$ is geometrically connected,
the comparison functor is an equivalence.
%(In other language, $q^*$ is a monadic functor.)
Indeed, it is easy to see that $\CCS(G\ab) \to \CCS_{G\der}(G)$ is full and faithful; to see that is it also essentially surjective, one begins with $\cs{L} \in \CCS(G)$ and $\nu : n^*\cs{L} \to p^*\cs{L}$ and builds $\cs{E}\in \CCS(G\ab)$ Zariski-locally by pull-back along local trivializations $U \to G\times_{G\ab} U$ of $q : G\to G\ab$ compatible with the $C$-action, glueing using isomorphisms inherited from the isomorphism $\nu$, and finally verifying that the result is a local system with the auxilliary data defining a commutative character sheaf. See appendix for details.\todo{Should I make the promised appendix, or is this paragraph enough?}

@@

\begin{lemma}
Every commutative character sheaf on $G$ is equivariant for the conjugation action of $G$ on $G$.
\end{lemma}

\begin{proof}
Let $a : G \times G \to G$ be the conjugation action of $G$ on $G$. Then $a = m \circ (m \times (\iota \circ p_1))$ and $m\op \circ (m \times (\iota \circ p_1)) = p_2$. Thus,
\begin{align*}
a^* \cs{L} 
&= (m \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
&= (m \times (\iota \circ p_1))^* m^* \cs{L}\\
&\iso (m \times (\iota \circ p_1))^* m\op^* \cs{L}\\
&= (m\op \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
&= p_2^*\cs{L}.
\end{align*}
\end{proof}

@@

\begin{lemma}
If $\cs{L}$ is a commutative character sheaf on $G$ then $\cs{L}\vert_C = (\EE)_C$.
\end{lemma}
\begin{proof}
 Consider the morphism $c:  G \times G \to C$ given by $c(g,h)= ghg^{-1}h^{-1}$.
This surjective morphism is smooth (it is a composition of smooth maps, since $G$ is smooth) with fibres
Let $j : C \hookrightarrow G$ be the inclusion.  
Then $j\circ c = m\circ (m \times (\iota\circ m\op)) : G \times G \to G$ is $(g,h) \mapsto gh g^{-1}h^{-1}$ while $m\op\circ (m \times (\iota\circ m\op))= e : G \times G \to G$ is $(g,h) \mapsto 1_G$. Thus,
\begin{align*}
c^* (\cs{L}\vert_C)
&=  (j\circ c)^*\cs{L} \\
&= (m\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
&= (m \times (\iota\circ m\op))^* m^* \cs{L} \\
&= (m \times (\iota\circ m\op))^* m\op^* \cs{L} \\
&= (m\op\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
&= e^* \cs{L}\\
&= (\EE)_{G\times G}\\
&= c^* ((\EE)_C).
\end{align*}
Since $c : G \times G \to C$ is faithfully flat, the functor $c^*$ is conservative.
\todo{I'm working on this   . . . \\ -CC}
Since $\cs{L} \to (\EE)_G$ induces $c^* (\cs{L}\vert_C) \iso c^* ((\EE)_C)$, this implies $\cs{L}\vert_C \iso (\EE)_C$. 
\end{proof}

@@

\section{Descent along smooth principal bundles}

>>>>

Recall \cite{cunningham-roe:13a}*{Def. 1.1} that a character sheaf on $G$ is a triple $\cs{L} \ceq (\gcs{L}, \mu, \phi)$,
where $\gcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, $\mu : \bm^* \gcs{L} \to \LxL$ is an isomorphism
of sheaves on $\bG \times \bG$, and $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an isomorphism of sheaves on $\bG$.
In \emph{loc. cit.}, $G$ was assumed to be commutative, but the same definition makes sense for non-commutative $G$.
We will denote the category of character sheaves on $G$ by $\CS(G)$.
\todo{I think we should hold the term `character sheaves for G', when $G$ is not commutative, in reserve, and not use it here for non-commutative $G$. So I might advocate going back to the full definition here. Or, we might introduce the term `rank-$1$ character sheaf, similar to what Masoud did  . . . \\ -CC}

@@

\begin{proposition}
Every commutative character sheaf on $G$ is equivariant for the conjugation action of $G$ on $G$. Conversely, if a [rank-$1$] character sheaf on $G$ is equivariant for conjugation, then $G$ is commutative. 
\end{proposition}

\begin{proof}
Let $a : G \times G \to G$ be the conjugation action of $G$ on $G$. Then $a = m \circ (m \times (\iota \circ p_1))$ while $m\op \circ (m \times (\iota \circ p_1)) = p_2$. Thus, if $m^*\cs{L} \iso m\op^*\cs{L}$ then
\begin{align*}
a^* \cs{L} 
&= (m \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
&= (m \times (\iota \circ p_1))^* m^* \cs{L}\\
&\iso (m \times (\iota \circ p_1))^* m\op^* \cs{L}\\
&= (m\op \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
&= p_2^*\cs{L}.
\end{align*}
Since the isomorphism $a^*\cs{L} \iso p_2^*\cs{L}$ is unique, $(\cs{L}, a^*\cs{L} \iso p_2^*\cs{L})$ is an equivariant commutative character sheaf.

Conversely, let $(\cs{L}, a^*\cs{L} \iso p_2^*\cs{L})$ be an equivariant [rank-$1$] character sheaf.
Observe that $m = a \circ (p_1\times m\op)$ while $p_2 \circ (p_1\times m\op) = m\op$. Thus, 
\begin{align*}
m^* \cs{L} 
&= (a \circ (p_1 \times m\op))^* \cs{L}\\
&= (p_1 \times m\op)^* a^* \cs{L}\\
&\iso (p_1 \times m\op)^* p_2^* \cs{L}\\
&= (p_2\circ (p_1 \times m\op))^* \cs{L}\\
&= m\op^* \cs{L}.
\end{align*}
Thus, $\cs{L}$ is a commutative character sheaf.
\end{proof}

@@

Let $G$ be a smooth group scheme.
Let $G\der \hookrightarrow G$ denote the closed subgroup generated by the commutator morphism $c: G\times G \to G$ given by $c(x,y) = xyx^{-1}y^{-1}$; see \cite{SGA3}*{{VI}$_B$, 7.2}.

\begin{lemma}
The quotient $q : G \to G\ab$ is a smooth $G\der$-torsor, and the coequalizer of $m, p : G\der \times G \to G$.
\end{lemma}

The quotient $q : G \to G\ab$ is the coequalizer of left $G\der$-multiplication $n : G\der\times G \to G$ and projection $p : G\der\times G \to G$.
\[
\begin{tikzcd}
G\der\times G
 \arrow{r}[shift left]{m}
  \arrow{r}[shift right,swap]{p}
&
G 
\arrow{r}{q}
& 
G\ab
\end{tikzcd}
\]
The morphism $q$ is surjective and smooth of relative dimension $\dim G\der$.

 \begin{theorem}\label{thm:descent}
 Let $G$ be a smooth group scheme over $\Fq$ 
 and let $q : G \to G\ab$ be its abelianization. 
 Then  
\[
q^*:  \CCS(G\ab) \longrightarrow \CCS(G)
\]
is an equivalence of rigid monoidal categories.
  \end{theorem}

\begin{proof}
It follows from the lemma that descent theory that $q$ is an 
effective descent morphism for the fibred category of commutative character sheaves on smooth group schemes; in other words, the canonical functor $\CCS(G) \to \CCS_{G\der}(G)$ is an equivalence. 
\todo{$\CCS \to \Sch{\Fq}$ is a fibred category. Is it also a stack?}

Consider the morphism $c:  G \times G \to G\der$ given by $c(g,h)= ghg^{-1}h^{-1}$.
This morphism is smooth (it is a composition of smooth maps, since $m : G \times G \to G$ is smooth) but

Let $j : C \hookrightarrow G$ be the inclusion.  
Then $j\circ c = m\circ (m \times (\iota\circ m\op)) : G \times G \to G$ is $(g,h) \mapsto gh g^{-1}h^{-1}$ while $m\op\circ (m \times (\iota\circ m\op))= e : G \times G \to G$ is $(g,h) \mapsto 1_G$. Thus,
\begin{align*}
c^* (\cs{L}\vert_C)
&=  (j\circ c)^*\cs{L} \\
&= (m\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
&= (m \times (\iota\circ m\op))^* m^* \cs{L} \\
&= (m \times (\iota\circ m\op))^* m\op^* \cs{L} \\
&= (m\op\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
&= e^* \cs{L}\\
&= (\EE)_{G\times G}\\
&= c^* ((\EE)_C).
\end{align*}
Since $c : G \times G \to C$ is faithfully flat, the functor $c^*$ is conservative.
\todo{I'm working on this   . . . \\ -CC}
Since $\cs{L} \to (\EE)_G$ induces $c^* (\cs{L}\vert_C) \iso c^* ((\EE)_C)$, this implies $\cs{L}\vert_C \iso (\EE)_C$.

Let $\CCS_{G\der}(G)$ be the category of commutative character sheaves $\cs{L}$ on $G$ equipped with an isomorphism $n^*\cs{L} \to p^*\cs{L}$ satisfying canonical coherence conditions.
Then $q^* : \CCS(G\ab) \to \CCS(G)$ factors through $\CCS_{G\der}(G)$. 
\[
\begin{tikzcd}
\CCS(G\der \times G)
& \arrow{l}[shift left,swap]{n^*}
  \arrow{l}[shift right]{p^*}
\CCS(G) 
&&\arrow{ll}[swap]{q^*} 
\CCS(G\ab) \arrow{dl}{\text{comparison}}\\
&& \arrow{ul}{\text{forget}} \CCS_{G\der}(G) & 
\end{tikzcd}
\]
To see this, let $\cs{E}$ be a commutative character sheaf on $G\ab$ and observe that $q^* \cs{E}$ is equipped with a canonical isomorphism $n^*(q^* \cs{E}) \to p^*(q^* \cs{E})$ given by
\[
n^* (q^*\cs{E}) \iso (q\circ n)^* \cs{E} = (q\circ p)^* \cs{E} \iso p^* (q^*\cs{E}).
\]
Moreover, since $q : G \to G\ab$ is a smooth principal $G\der$-bundle and $G\der$ is geometrically connected,
the comparison functor is an equivalence.
%(In other language, $q^*$ is a monadic functor.)
Indeed, it is easy to see that $\CCS(G\ab) \to \CCS_{G\der}(G)$ is full and faithful; to see that is it also essentially surjective, one begins with $\cs{L} \in \CCS(G)$ and $\nu : n^*\cs{L} \to p^*\cs{L}$ and builds $\cs{E}\in \CCS(G\ab)$ Zariski-locally by pull-back along local trivializations $U \to G\times_{G\ab} U$ of $q : G\to G\ab$ compatible with the $C$-action, glueing using isomorphisms inherited from the isomorphism $\nu$, and finally verifying that the result is a local system with the auxilliary data defining a commutative character sheaf. See appendix for details.

@@

@@

@@

\section{Descent along smooth fibrations}

Let $G$ be a group scheme acting on $X$ by $m : G \times X \to X$.

A principal $G$-bundle $f : X\to Y$ is a coequalizer of $m$ and projection $G\times X \to X$  
which is locally trivial in the following sense.
First, there is an open covering $\{ V_n\}$ of $Y$ such that, for each $V$ in this covering, the lower coequalizer diagram is a base change of the one above
\[
\begin{tikzcd}
G\times X
 \arrow{rr}[shift left]{m}
  \arrow{rr}[shift right,swap]{\text{proj'n}}
&& X \arrow{r}{f} &  Y\\
G\times  (G\times V) \arrow{u}
 \arrow{rr}[shift left]{\text{mult'n in $G$}}
  \arrow{rr}[shift right,swap]{\text{proj'n}}
&& G\times V \arrow{u}  \arrow{r} &  \arrow{u} V;
\end{tikzcd}
\]

and the following diagram commutes
\[
\begin{tikzcd}
G\times  f^{-1}(V)
 \arrow{r}[shift left]{m}
  \arrow{dr} 
& f^{-1}(V) \arrow{r} \arrow{d}{t_V} &  V \\
& G\times V \arrow{ur} & 
\end{tikzcd}
\]

and isomorphisms ${t}_n : f^{-1}{V}_n \to {G}\times {V}_n$ such that  ${f}$ is given locally by ${f}_n = p \circ {t}_n$ (so ${f}_n : {f}^{-1}{Y}_n \to {Y}_n$) and the action ${m}_{X}$ of ${G}$ on ${X}$ is given locally by ${t}_n \circ {m}_n =  ({m} \times \id) \circ (\id\times{t}_n)$ (so ${m}_n : {G}\times{f}^{-1}{Y}_n \to {f}^{-1}{Y}_n$).

Let $\Loc^1(X)$ be the category of rank-$1$ local systems on $X$ and let $\Loc_G^1(X)$ be the category of $G$-equivariant rank-$1$ local systems on $X$.

\begin{proposition}
Let $G$, $X$ and $Y$ be smooth.
Let $f : X \to Y$ be a $G$-torsor.
Then the comparison functor, pictured below,
\[
\begin{tikzcd}
%\Loc^1(G \times X)
%& \arrow{l}[shift left,swap]{m^*}
%  \arrow{l}[shift right]{p^*}
\Loc^1(X) 
&&\arrow{ll}[swap]{f^*} 
\Loc^1(Y) \arrow{dl}{\text{comparison}}\\
& \arrow{ul}{\text{forget}} \Loc^1_G(X) & 
\end{tikzcd}
\]
is an equivalence.
\end{proposition}

\begin{proof}
This is well-known. We include a proof only for completeness.

To simplify notation slightly, set ${X}_n \ceq {f}^{-1}{Y}_n$; also, let ${j}_n : {Y}_n \to {Y}$ and ${i}_n : {X}_n \to {X}$ denote inclusions.

Then $f : X \to Y$ is a smooth, regular epimorphism with kernel pair $m, p: G\times X\to X$, and t

Consider the following commuting diagram:
\[
\begin{tikzcd}
H\times X \arrow{d}{\id\times f} \arrow{r}{m_X}&\to X\arrow{d}{f}\\
H\times Y \arrow{r}{m_Y} &\to Y\\
H\times X \arrow{r}{p_2} \arrow{u}{\id\times f} &\to X \arrow{u}{f}
\end{tikzcd}
\]
Thus,
\[
\begin{aligned}
m_X^*[\dim H] f^*[d] A
&\iso (f\circ m_X)^* [d+\dim H]A  &\\
&\iso (m_Y\circ (\id\times f))^*[d+\dim H]A & \text{$f$ is equivariant}\\
&\iso (\id\times f)^*[d] m_Y^*[\dim H] A &\\
&\iso  (\id\times f)^*[d] p_2^*[\dim H] A &\text{$A$ is $H$-equivariant}\\
&\iso  (p_2\circ (\id\times f))^*[d+\dim H] A &\\
&\iso (f\circ p_2)^*[d+\dim H]A & \\
&\iso p_2^*[\dim H] f^*[d]A. &
\end{aligned}
\]
This completes the proof that $f^*[d]A$ is an $H$-equivariant perverse sheaf on $X$.

Let $\mathcal{F} = {f}^*[\dim{P}] \mathcal{G}$.

To show that $\mathcal{F}$ is equivariant we must find an isomorphism $\mu : {m}^* \mathcal{F} \to p^* \mathcal{F}$ in $D^b_c({P}\times{X}, \EE)$ such that ${e}^*\mu = \id_{\mathcal{F}}$, where ${e} : {X} \to {P}\times{X}$ is the section defined by $x \mapsto (1,x)$. To see this, consider the restriction of ${m}^* \mathcal{F}$ to ${P}\times{X}_n$:
\begin{eqnarray*}
({m}^* \mathcal{F})\vert_{{P}\times {X}_n}
	&=& (\id\times {i}_n)^* {m}^* {f}^* \mathcal{G} [\dim{P}]\\
	&\iso& ({f}\circ {m} \circ \id\times {i}_n)^* \mathcal{G} [\dim{P}]\\
	&=& ({f} \circ {i}_n \circ {m}_n)^* \mathcal{G} [\dim{P}].
\end{eqnarray*}
On the other hand, the restriction of $p^* \mathcal{F}$ to ${P}\times{X}_n$ is 
\begin{eqnarray*}
(p^* \mathcal{F})\vert_{{P}\times {X}_n}
	&=& (\id\times {i}_n)^* p^* {f}^* \mathcal{G} [\dim{P}]\\
	&\iso& ({f}\circ p \circ \id\times {i}_n)^* \mathcal{G} [\dim{P}]\\
	&=& ({f} \circ {i}_n \circ p)^* \mathcal{G} [\dim{P}].
\end{eqnarray*}
Since ${f} \circ {i}_n \circ {m}_n = {f} \circ {i}_n \circ p$, we have $({m}^* {\mathcal{F}})\vert_{{P}\times {X}_n} \iso (p^* \mathcal{F})\vert_{{P}\times {X}_n}$. Since $\cup_n {P}\times{X}_n$ is an open cover for ${P}\times{X}$, this gives the isomorphism we seek.

Next, suppose $\mathcal{F} \in \obj{\mathcal M}{X}$ is equivariant; thus, $\mathcal{F} \in \obj{\mathcal M}_{P}{X}$. Let $\mathcal{F}_n$ denote the restriction of $\mathcal{F}$ to ${X}_n$.

Recall that ${m}: {P}\times{X} \to {X}$ is given locally by ${m}_n : {P}\times {X}_n \to {X}_n$, as above. Restricting the isomorphism $\mu_{\mathcal{F}} : {m}^* \mathcal{F} \to p^* \mathcal{F}$ to ${P}\times{X}_n$ yields the isomorphism $\mu_{\mathcal{F}_n} : {m}_n^* \mathcal{F}_n \to p^* \mathcal{F}_n$. Thus, $\mathcal{F}_n$ is an equivariant perverse sheaf. Now, let ${e}_n : {Y}_n \to {X}_n$ be the section of ${f}_n : {X}_n \to {Y}_n$ corresponding to $1\in {P}(\Fq)$ (so ${e}_n$ is the unique morphism of varieties such that $({t}_n \circ {e}_n) (y) = (1,y)$). Define
\begin{equation}\label{equation: torsor 5}
	\mathcal{F}'_n \ceq {e}_n^* \mathcal{F}_n [-\dim{P}].
\end{equation}
Then $\mathcal{F}'_n \in \obj D^b_c({Y}_n, \EE)$. By standard glueing arguments, the collection of $\mathcal{F}'_n \in\obj D^b_c({Y}_n, \EE)$, as ${Y}_n$ ranges over the open cover of ${Y}$ fixed above, uniquely determines an object $\mathcal{G}$ of $D^b_c({Y}, \EE)$.

It remains to be shown that $\mathcal{G}$ is a perverse sheaf. Again, we work locally. For each such $n$,
\begin{eqnarray*}
{f}_n^*[\dim{P}] \mathcal{F}'_n 
	&=& {f}_n^*[\dim{P}] {e}_n^* \mathcal{F}_n [-\dim{P}]\\
	&\iso& ({e}_n\circ {f}_n)^* \mathcal{F}_n.
\end{eqnarray*}
Let ${u}_n : {X}_n \to {P}\times{X}_n$ be the section of ${m}_n : {P}\times{X}_n \to {X}_n$ corresponding to $1$ (so ${u}_n$ is the unique morphism of varieties such that $(\id\times{t}_n)\circ {u}_n \circ {t}_n^{-1} (h,y) = (h,1,y)$). The domain of ${u}_n^*\mu_{\mathcal{F}_n}$ is ${u}_n^*{m}_n^* \mathcal{F}_n \iso ({m}_n \circ {u}_n)^* \mathcal{F}_n = \mathcal{F}_n$, since ${u}_n$ is a section of ${m}_n$; the codomain of ${u}_n^* \mu_{\mathcal{F}_n}$ is ${u}_n^* p^* \mathcal{F}_n \iso (p\circ {u}_n)^*\mathcal{F}_n$. Since $p\circ {u}_n = {e}_n \circ {f}_n$, it follows that 
\[
{u}_n^* \mu_{\mathcal{F}_n} : \mathcal{F}_n \to {f}_n^*[\dim{P}] \mathcal{F}'_n
\]
is an isomorphism in $D^b_c({X}_n, \EE)$. By \cite[Prop~4.2.5]{BBD} and the fact that ${\mathcal M}{X}_n$ is stable in $D^b_c({X}_n, \EE)$ under isomorphisms, it follows that $\mathcal{F}'_n \in \obj {\mathcal M}{Y}_n$. By standard glueing arguments, the collection of isomorphisms ${u}_n^* \mu_{\mathcal{F}_n} \in \mor{\mathcal M}{X}_n$, as ${X}_n$ ranges over the open cover of ${X}$ fixed above, uniquely determines an isomorphism in \[
\Hom_{D^b_c({X}, \EE)}(\mathcal{F},{f}^*[\dim{P}] \mathcal{G}).
\]  
From \cite[Prop~4.2.5]{BBD}  it follows that $\mathcal{G}\in \obj{\mathcal M}{Y}$. This completes the proof of Proposition~\ref{proposition: torsor}.
\end{proof}

\begin{proposition}\label{proposition: more torsor}
Let ${f} : {X} \to {Y}$ be a principal fibration with group ${P}$ and suppose ${P}$ is connected. Then ${f}^*[\dim{P}] : {\mathcal M}{Y} \to {\mathcal M}_{P}{X}$ is an equivalence of categories and ${\mathcal M}_{P}{X}$ is a thick subcategory of ${\mathcal M}{X}$.
\end{proposition}

\begin{proof}
By \cite[Prop~4.2.5]{BBD} we know that ${f}^*[\dim{P}] : {\mathcal M}{Y} \to {\mathcal M}{X}$ is full and faithful. Let $\mathcal{G}$ be a perverse sheaf on ${Y}$. From the proof of Proposition~\ref{proposition: torsor} we have seen that $\mathcal{F} \ceq {f}^*[\dim{P}] \mathcal{G}$ is an equivariant perverse sheaf on ${X}$ and that ${f}^*[\dim{P}] \phi$ is an equivariant morphism in ${\mathcal M}{X}$ for each morphism $\phi$ in ${\mathcal M}{Y}$. Thus, ${f}^*[\dim{P}]$ is a functor from ${\mathcal M}{Y}$ to ${\mathcal M}_{P}{X}$. Thus, ${f}^*[\dim{P}] : {\mathcal M}{Y} \to {\mathcal M}_{P}{X}$ is full and faithful. Proposition~\ref{proposition: torsor} tells us that this functor is essentially surjective. Thus, ${f}^*[\dim{P}]$ is an equivalence. The last clause of Proposition~\ref{proposition: more torsor} follows from \cite[4.2.6]{BBD}.
\end{proof}

\begin{definition}\label{definition: descent}
Let ${f} : {X} \to {Y}$ be a principal fibration with group ${P}$ and suppose ${P}$ is connected. Let ${f}_\# : {\mathcal M}_{P}{X} \to {\mathcal M}{Y}$ denote the adjoint of the equivalence ${f}^*[\dim{P}] : {\mathcal M}{Y} \to {\mathcal M}_{P}{X}$ (see Proposition~\ref{proposition: more torsor}). In particular, ${f}_\# : {\mathcal M}_{P}{X} \to {\mathcal M}{Y}$ is an equivalence of categories.
\end{definition}

\begin{corollary}
Suppose $H$ is a connected group acting smoothly on $X$.
If $A\in {\mathcal M} X$ is $H$-equivariant and $B\in {\mathcal M} X$ is a subquotient of $A$, then $B$ is also $H$-equivariant.
\end{corollary}

\begin{proof}
(Following \cite[(1.9.1)]{CS}.)
Let the action of $H$ on $Y$ is given by $m : H\times X \to X$. This is a smooth morphism with connected fibres, by hypothesis. Thus, $m^*[\dim H]$ is an equivalence of categories, by Proposition~\ref{proposition: more torsor}.  Since equivalences take epimorphisms to epimorphisms and monomorphisms to monomorphisms, it follows that $m^*[\dim H]B$ is a subquotient of $m^*[\dim H]A$. Since $A$ is an $H$-equivarient perverse sheaf on $X$, we have $m^*[\dim H]A \iso p_2^*[\dim H]A$. On the other hand, $p_2 : H\times X \to X$ is also a smooth morphism with connected fibres of dimension $H$, so by Proposition~\ref{proposition: more torsor}, $p_2^*[\dim H]$ identifies ${\mathcal M}_H X$ with a thick subcategory of ${\mathcal M} (H\times X)$. Since $m^*[\dim H]B$ is a subquotient of $p_2^*[\dim H]A$, it follows that there is some $C\in {\mathcal M} X$ such that $p_2^*C \iso m^*[\dim H]B$ restricting this isomorphism from $H\times X$ to $\{ e\} \times X$ (on which $m$ and $p_2$ agree), yields $C\iso B$. Thus, $p_2^*B \iso m^*[\dim H]B$, from which is follows that $B$ is $H$-equivariant.
\end{proof}
